\section*{Appendix}

In this part, several interesting constructions are listed, 
while others are left in \mintinline{bash}|./libs/Init/Prelude.v|.

\subsection*{Boolean}
\begin{center}
\begin{minted}{coq}
Inductive True : Type :=
| I : True.

Inductive False : Type :=.

Inductive and (A : Type) (B : Type) : Type :=
| conj : A -> B -> and A B.

Inductive or (A : Type) (B : Type) : Type :=
| or_introl : A -> or A B
| or_intror : B -> or A B.
\end{minted}
\end{center}

\subsection*{Logic}
\begin{center}
\begin{minted}{coq}
Definition If_then_else (P : Type) (Q : Type) (R : Type) : Type :=
    or (and P Q) (and (not P) Q).

Definition not (A : Type) : Type :=
    A -> False.

Definition iff (A : Type) (B : Type) : Type :=
    and (A -> B) (B -> A).

Inductive ex (A : Type) (P : A -> Type) : Type :=
| ex_intro : forall (x : A), P x -> ex A P.

Inductive eq (A : Type) (x : A) : A -> Type :=
| eq_refl : eq A x x.
\end{minted}
\end{center}

\subsection*{Natural Number}
\begin{center}
\begin{minted}{coq}
Inductive nat : Type :=
| O : nat
| S : nat -> nat.

Fixpoint plus (n : nat) (m : nat) : nat :=
    match n as n0 in nat return nat with
    | O => m
    | S n1 => S (plus n1 m)
    end.

Fixpoint multiply (n : nat) (m : nat) : nat :=
    match n as n0 in nat return nat with
    | O => O
    | S n1 => plus m (multiply n1 m)
    end.

Fixpoint power (n : nat) (m : nat) : nat :=
    match m as m0 in nat return nat with
    | O => S O
    | S m1 => multiply n (power n m1)
    end.
\end{minted}
\end{center}

\subsection*{List}
\begin{center}
\begin{minted}{coq}
Inductive list (T : Type) : Type :=
| nil : list T
| cons : T -> list T -> list T.

Inductive iliist (T : Type) : nat -> Type :=
| inil : ilist T O
| icons : forall (n : nat), T -> ilist T n -> ilist T (S n).
\end{minted}
\end{center}
