\section{Tactic}
Although proofs can be automatically checked given the system above, it requires user to input the whole
term of the specific type, which is tedious, exhaustive, mostly unintuitive.\par
So in this part, we introduced some tactics into the system 
to assist users in better writing the proof. With the help of
tactics, the proof becomes more human-readable and intuitive.\par

\subsection{\it Apply}

\subsection{\it Destruct}

\subsubsection*{Usage}
\begin{itemize}
\item ${\it destruct}\ \tt x.$ : 
\item ${\it destruct}\ \tt t.$ :
\end{itemize}

\subsubsection*{Implementation}

\subsection{\it Equivalence}

\subsection{\it Exact}

\subsection{\it Exists}

\subsection{\it Induction}

\subsection{\it Intro}

If the current goal is a dependent product $\tt \forall x:T,\ U$, \textit{intro} puts 
$\tt x:T$ in the context, and the new subgoal is $\tt U$.\par
If the current goal is a non-dependent product $\tt \forall \_:T,\ U$, \textit{intro} renames
$\tt \_$ into $\tt s$ not in $\tt T,U$ and context. Then put $\tt s:T$ in the context, 
and the new subgoal becomes $\tt U$.

\subsubsection*{Usage}
\begin{itemize}
\item ${\it intro}\ .$ : introduce the outmost augument of current goal and rename them automatically.
\item ${\it intro}\ a_1\ a_2\ \cdots\ a_n.$ : introduce $n$ outmost auguments of current goal and
try to rename them into $a_1,a_2,\cdots,a_n$.
\end{itemize}

\subsubsection*{Implementation}
Since the context automatically preserves the index, we
can safely move the auguments out into the context without worrying about the index.

\subsection{\it Intros}

If the current goal is a dependent (or non-dependent) product with $m$ auguments, namely,
$\tt \forall x_1:T_1,\ \forall x_2:T_2,\ \cdots\ \forall x_m:T_m,\ U$ where $\tt U$ is not a product type.
Then \textit{intros} will put these $m$ auguments into the context and rename automatically if necessary.

\subsubsection*{Usage}
\begin{itemize}
\item ${\it intros}.$ : introduce all the augument of current goal and rename them automatically.
\end{itemize}

\subsubsection*{Implementation}
Keep calling {\it intro} until all the goal has no auguments.

\subsection{\it Left}

\subsection{\it Reflexivity}

\subsection{\it Rewrite}

\subsection{\it Right}

\subsection{\it Simpl}

\subsection{\it Split}

\subsection{\it Symmetry}

\subsection{\it Unfold}

