\section{Top Level}

In top level, the system maintains the interaction with user and
adds the user input, namely, \textit{Axiom}, \textit{Definition}, \textit{Fixpoint}, and \textit{Inductive Definition}, 
into the context.\par
It is also in this part, the inductive rule forms.

\subsection{Acceptance of command}
\subsubsection{Axiom}
After parsing and checking, the command will be like
$$
\tt Ax\ \ {\it name\ term},
$$ 
where {\it term} denotes the type of this axiom.
Since it is an axiom, we do not have to (sometimes can not) build the corresponding term.\par
Just build the corresponding term as {\it Nothing} then put it into the context.

\subsubsection{Definition}
After parsing and checking, the command will be like
$$
\tt Def\ \ {\it name\ term2\ term1},
$$
where {\it term2} is the type of {\it term1}.\par
Simply bind the name, term, type together and put it into the context.

\subsubsection{Fixpoint}
After parsing and checking, the command will be like
$$
\tt Fix\ {\it name }\ \left(\lambda {\it f}:{ \it term1},\ {\it term2}\right),
$$
where {\it term1} is the type of {\it term2} and it is a recursive function of {\it f}.\par 
Since this recursive function has passed all the type check and safety check, we can safely use it without worrying termination
problem.
On the other hand, whether it is a {\it Fixpoint} definition will not influence any reduction, because the reduction
always finds the term in context according to its index.\par
So simply remove the {\it Fixpoint} mark and put it into the context.

\subsubsection{Inductive Definition}
After parsing and checking, the command will be like
$$
\tt Ind\ \ {\it name\ p\ term2\ term1\ constructors},
$$
where {\it p} is the number of parameters of the inductive type, {\it term1} is the type of the inductive definition,
and {\it term2} is the corresponding term.\par
Apart from the ordinary operation, we also need to add inductive rule, which is actually a type theory view of mathematical
induction. Since the proof of a claim becomes a term of certain type, the induction rule is a term offering inductive scheme.\par
For example,
\begin{center}
\begin{minted}{coq}
Inductive nat : Type := 
| O : nat
| S : nat -> nat.

(* build inductive rule*)

fun (P:nat -> Type)(f:P O)(f0:forall (n:nat), P n -> P (S n))
    fix F (n:nat) : P n :=
        match n as n0 in nat return (P n0) with
        | O => f
        | S n0 => f0 n0 (F n0)
        end
:
forall (P:nat -> Type), P O -> 
    (forall (n:nat), P n -> P (S n)) ->
        forall (n:nat), P n
\end{minted}
\end{center}
The intuition here is that for a proposition \mintinline{coq}|P|,
\begin{itemize}
\item it is true on \mintinline{coq}|O|;
\item if it is true on \mintinline{coq}|n|, then it is true on \mintinline{coq}|S n|.
\end{itemize}
Then it is true on all term of \mintinline{coq}|nat| type, which is reasonable according 
mathematical induction.\par
Basically, to build such term, we should build weakened assumptions for all constructors first, 
like the \mintinline{coq}|f|,
\mintinline{coq}|f0| above. After that, the final proposition which applies to all the terms of such inductive type
shall come out, like the \mintinline{coq}|F| above.\par
Every occurrence of the inductive type on the constructors demands a verification of the proposition,
which explains why for constructor \mintinline{coq}|S : nat -> nat|, which depends on a \mintinline{coq}|nat| term, 
the weakened assumption is \mintinline{coq}|f0 : forall (n:nat), P n -> P (S n)|.\par
The reason why the inductive rule of \mintinline{coq}|nat| requires {\it Fixpoint} is that some constructors of it
rely on the term of type \mintinline{coq}|nat|. Here is a case which do not need recursive function.
\begin{center}
\begin{minted}{coq}
Inductive eq (T : Type) (x : T) : T -> Type :=
| eq_refl : eq T x x.

(* build inductive rule*)

fun (T:Type) (x:T) (P:forall (t:T) (_:eq T x t), Type) 
    (f:P x (eq_refl T x)) (t:T) (e:eq T x t) => 
        match e as e0 in eq _ _ a0 return (P a0 e0) with 
        | eq_refl _ _ => f
        end
: 
forall (T:Type) (x:T) (P:forall (t:T) (_:eq T x t), Type) 
    (f:P x (eq_refl T x)) (t:T) (e:eq T x t),
        P t e
\end{minted}
\end{center}
Sadly, we have to admit that because of the lack of references, time, and energy,
the induction rule in our system is not complete.
The inductive definition acceptable to our system must satisfy:\par
Assume the inductive type is $\tt A_1\to A_2\to \cdots A_n$, then $\tt A_k$ must be
any one of the following
\begin{itemize}
\item A ordinary term, like \mintinline{coq}|Type|, \mintinline{coq}|T|.
\item An application, like \mintinline{coq}|P n|.
\item An inductive type, like \mintinline{coq}|nat|, \mintinline{coq}|eq T x y|.
\end{itemize}
Others like product type \mintinline{coq}|U -> V| is not supported.

\subsection{Requests to the environment}
\subsubsection{\tt Print \sl ident}
This command displays on the screen information about the declared or defined object referred by {\sl ident}.
\subsubsection{\tt Check \sl term}
This command displays the type of {\sl term}.

\subsection{Top Loop}
The main work flow of our top level loop:
\subsubsection*{Reading raw input}
The Mini Prover will read the user's input until a dot('.'), and any further input in the same line will be abandoned.
\subsubsection*{Parsing}
The raw input will be parsed without nameless representation.

Here is an example, the raw input
\begin{center}
\begin{minipage}{0.7\textwidth}
\begin{minted}{coq}
(* raw input *)
Fixpoint plus (n:nat) (m:nat) : nat :=
match n as n0 in nat return nat with
| O => m
| S n0 => S (plus n0 m)
end.
\end{minted}
\end{minipage}
\end{center}
will be parsed as the AST
\begin{center}
\begin{minipage}{0.9\textwidth}
\begin{minted}{haskell}
Fix "plus"
  ( TmFix (-1)
    ( TmLambda "plus"
      ( TmProd "n" ( TmVar "nat" )
        ( TmProd "m" ( TmVar "nat" ) ( TmVar "nat" )))
      ( TmLambda "n" ( TmVar "nat" )
        ( TmLambda "m" ( TmVar "nat" )
          ( TmMatch (-1) ( TmVar "n" ) "n0" [ "nat" ]
            ( TmVar "nat" )
            [ Equation [ "O" ] ( TmVar "m" )
            , Equation [ "S", "n0" ]
              ( TmAppl
                [ TmLambda "n" ( TmVar "nat" )
                  ( TmAppl [ TmVar "S", TmVar "n" ])
                , TmAppl [ TmVar "plus", TmVar "n0", TmVar "m" ]])])))))
\end{minted}
\end{minipage}
\end{center}
\subsubsection*{Duplicate global name checking}
After parsing, we can get the name of the input command, and the name should not be the same with
any defined or declared object in the environment.
\subsubsection*{Name checking}
Before building the nameless representation, there should be no unbounded name in the AST.
\subsubsection*{Nameless representation building}
If all names are bounded, we can build the nameless representation. The variable pointed to
a type constructor or a term constructor will be unfolded to its functional representation.

Here is an example, the nameless AST will be built for the previous AST:
\begin{center}
\begin{minipage}{0.9\textwidth}
\begin{minted}{haskell}
Fix "plus"
( TmFix (-1)
  ( TmLambda "plus"
    ( TmProd "n" ( TmIndType "nat" [])
      ( TmProd "m" ( TmIndType "nat" []) ( TmIndType "nat" [])))
    ( TmLambda "n" ( TmIndType "nat" [])
      ( TmLambda "m" ( TmIndType "nat" [])
        ( TmMatch 0 ( TmRel "n" 1 ) "n0" [ "nat" ] ( TmIndType "nat" [])
          [ Equation [ "O" ] ( TmRel "m" 0 )
          , Equation [ "S", "n0" ]
            ( TmAppl 
              [ TmLambda "n" ( TmIndType "nat" [])
                ( TmConstr "S" [ TmRel "n" 0 ])
              , TmAppl
                [ TmRel "plus" 3
                , TmRel "n0" 0
                , TmRel "m" 1 ]])])))))
\end{minted}
\end{minipage}
\end{center}
\subsubsection*{Positivity Checking(Inductive Definition Only)}
For an inductive definition, after building it's nameless representation, the positivity
could be checked.
\subsubsection*{Termination Checking}
All subterms with fixpoint definitions will be checked if they are terminating. After checking,
annotations for the indices of decreasing variables will be added to the AST.
\subsubsection*{Type checking}
Before actually dealing with the command, the top level will check if it's a well-typed command.
\subsubsection*{Processing the command}
The definitions and declarations will be processed as described before. And an assertion will lead to the proof editing mode.

